Compact linkable ring signatures and applications

### 2019-07-26 paper/iacr.tex
Updates to CLSAG paper

\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ and there exists a pair of indices $\ell$ and $\ell^\prime$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
$\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
\end{description}

@@

\item $\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the \textit{linkability tag} or \textit{key image} $\mathfrak{T}$, and auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$:
\begin{align*}
\mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_1(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
\end{align*}

@@

We use the following in the next definition. Let $n(-)$ be a positive polynomial. Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle. Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$. Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$. Let $T_C$ be the set of all linkability tags that appear as output from such a query. Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $pk_\ell \in \underline{\textbf{pk}} \cap \underline{\textbf{pk}^\prime}$ and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.

@@

@@

\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any computationally unbounded PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
\begin{enumerate}
\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \left(\mathbb{Z}/p\mathbb{Z}\right)^3$ uniformly and independently for $i=1, \ldots, n$. The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.

>>>>

\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
$\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
\end{description}

@@

\item $\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the \textit{linkability tag} or \textit{key image} $\mathfrak{T}$, and auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$:
\begin{align*}
\mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
\end{align*}

@@

We use the following in the next definition. Let $n(-)$ be a positive polynomial. Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle. Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ from the list of challenge keys and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$. Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$. Let $T_C$ be the set of all linkability tags that appear as output from such a query. Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $\underline{\textbf{pk}^\prime}$ is a matrix of challenge key vectors (i.e.\ each column is in $\textbf{pk}$) and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$ and $\mathfrak{T}$ is the linkability tag for the $\ell^{th}$ key in $\underline{\textbf{pk}}^\prime$.

@@

\begin{remark}
Note that if the corruption oracle merely acted by computing arbitrary discrete logarithms, then an adversary could do the following: take some target $\textbf{pk}$ from the challenge set, apply a permutation to the coordinates of $\textbf{pk}$, pass the permuted key through $\mathcal{CO}$, obtain the discrete logarithm of the first (signing) key of $\textbf{pk}$, compute the linkability tag for this signing key, and lastly produce a signature using $\texttt{Sign}$.

Such a signature would pass validation and not be described as a forgery according to our definition. Our definition avoids this problem by requiring the corruption oracle only be queried with challenge keys. This way, a corruption oracle can be simulated for the black box execution of $\texttt{A}$.
\end{remark}

@@

\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
\begin{enumerate}
\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \left(\mathbb{Z}/p\mathbb{Z}\right)^3$ uniformly and independently for $i=1, \ldots, n$. The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.
